%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Laila Chavez}
\address{ Seattle, WA 98109}
\contacts{(562) 552-0620 \linebreak lailamay.chavez@gmail.com}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Software Engineer}{VueMed}{June 2023 -- December 2023}			
			\begin{itemize}
				\item Authored comprehensive onboarding documentation to streamline the integration process for new team members.
				\item Completed Azure Runbooks migrations within Microsoft Azure Services, optimizing cloud operations and improving system reliability.
				\item Successfully piloted an initiative to implement CI/CD processes by automating application deployments to on premise servers using Microsoft Azure Pipelines and Deployment groups, improving the reliability of deploying application updates to customers. 
				\item Conducted extensive research and developed detailed Git workflow documentation, standardizing development practices for the growing development team.
				\item Debugged and resolved critical errors in a .NET project, specifically issues related to non-binary files not included in .gitignore, enhancing project stability.
				\item Engaged with internal dashboard application users to identify bugs, and efficiently translated feedback into actionable Jira bug stories.
				\item Implemented advanced Blazor and C# code to augment and introduce new features in internal application, driven by user feedback, significantly boosting application performance and user satisfaction.
				\item Led a pilot project from design to production, providing a medical organization with ESL labels for inventory management, showcasing strong project management skills and client-focused solutions.
				\item Cleaned client data from Excel spreadsheets and skillfully created a structured SQL database, enhancing internal usage efficiency. 
				\item Designed ESL labels utilizing data from client's inventory item master, demonstrating exceptional attention to detail and client-specific customization.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Engineer}{Accenture}{March 2021 -- May 2023}	
			\begin{itemize}
				\item Optimized a monolithic application by breaking it up into microservices, resulting in easier deployments and testing.
				\item Created integration, end-to-end, and unit tests to ensure application and code quality.
				\item Implemented Test Driven Development to develop clean and concise code.
				\item Collaborated closely with product owners and internal teams to ensure the solution meets customer standards.
				\item Used technologies such as Angular, React, and Next.js to create modern full-stack web applications.
				\item Modernized web applications using optimization techniques like server side rendering to improve lighthouse performance scores by 25\% providing better user experience.
				\item Utilized agile methodologies to create stories during the software development life cycle using tools such as Jira and Confluence.
				\item Wrote various onboarding documentation to help new developers bootstrap quicker to projects.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Engineer Intern}{C4ADS}{September 2020 -- Dec 2020}		
			\begin{itemize}
				\item Used Front-end libraries like React to Modernize educational applications.
				\item Translated customer requirements into a user-friendly web application.
				\item Updated educational app user interface to include quiz like functionality using React quiz components.
				\item Refactored components to improve usability and readability of the code.
				\item Used tools such as SwaggerHub to document third party API endpoints for internal team dashboard.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Engineer Intern}{CodeDay}{July 2020 -- August 2020}		
			\begin{itemize}
				\item Lead a greenfield project to create a full-stack web application to help middle school students with finance management.
				\item Implemented object-oriented methodologies to create a web application using Django.
				\item Created schemas using SQLite and SQL to model student and teacher relationships for web applications.
				\item Implemented MVC practices to ensure separation of concerns between the front-end and the back-end.
				\item Presented application to key stakeholders to determine user adaptability.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Seattle, WA}{North Seattle College}{Fall 2016 -- June 2020}
			\begin{itemize}
				\item M.S.E. in Computer and Information Science, May 2005. GPA: 3.6
				\item B.S.E. in Computer Science Engineering with Minor in Mathematics, May 2005.  In-major GPA: 3.4.
				\item Graduate Coursework: Software Foundations; Computer Architecture; Algorithms; Artificial Intelligence; Comparison of Learning Algorithms; Computational Theory.
				\item Undergraduate Coursework: Operating Systems; Databases; Algorithms; Programming Languages; Comp. Architecture; Engineering Entrepreneurship; Calculus III.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{Multi-User Drawing Tool} (2004). Electronic classroom where multiple users can view and simultaneously draw on a “chalkboard” with each person’s edits synchronized.  C++, MFC
				\item \textbf{Synchronized Calendar} (2003 – 2004). Desktop calendar with globally shared and synchronized calendars, allowing users to schedule meetings with other users.  C\#.NET, SQL, XML
				\item \textbf{Operating System} (2002).  UNIX-style OS with scheduler, file system, text editor and calculator. C
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Additional Experience and Awards}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Instructor (2003 – 2005):} Taught two full-credit Computer Science courses; average ratings of 4.8 out of 5.0.
				\item \textbf{Third Prize, Senior Design Projects:} Awarded 3rd prize for Synchronized Calendar project, out of 100 projects.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item C++; C; Java; Objective-C; C\#.NET; SQL; JavaScript; XSLT; XML (XSD) Schema 
				\item Visual Studio; Microsoft SQL Server; Eclipse; XCode; Interface Builder
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}

